\mtexe{3.1.5}
\begin{proof}
	Let $U \subseteq X$ and $V \subseteq Y$ be affine open neighborhoods. Note that we have a commutative diagram:
	\[ \begin{tikzcd} U \times_k V \arrow[r, "\ast"] \arrow[d, "\ast"] & U \times_k Y \arrow[r] \arrow[d, "\ast"] & U \arrow[d, "\ast"] \\ X \times_k V \arrow[r, "\ast"] \arrow[d] & X \times_k Y \arrow[r] \arrow[d] & X \arrow[d] \\ V \arrow[r, "\ast"] & Y \arrow[r] & \Spec k \end{tikzcd} \]
	In fact, each of the smaller subsquares is a fiber product by repeated application of the fact that $(A \times_S B) \times_B C \cong A \times_S C$ with the appropriate morphisms. Further, note that the morphisms $U \hookrightarrow X$ and $V \hookrightarrow Y$ are open immersions and since this is preserved by base change, each morphism above labelled ``$\ast$'' is an open immersion. Finally, the composition of open immersions is an open immersion, so we get that $U \times_k V$ is an open subset of $X \times_k Y$. But the former is the fiber product of affine schemes over an affine base scheme, so is itself affine. In fact, it is the tensor product of two finitely generated $k$-algebras, so is itself a finitely generated $k$-algebra. Doing this for all $U$ in a cover of $X$ and all $V$ in a cover of $Y$ shows that $X \times_k Y$ is itself an algebraic variety, and so $\dim(X \times_k Y) = \dim(U \times_k V)$, $\dim X = \dim U$, and $\dim Y = \dim V$.
	
	So, we have reduced to the affine case. Namely, suppose $A,B$ are finitely generated $k$-algebras. Then we can choose noether normalizations so that $k[x_1,\ldots,x_n] \subseteq A$ and $k[y_1,\ldots,y_m] \subseteq B$ are finite extensions. Tensoring over $k$ gives that $A \otimes_k B \supseteq k[x_1,\ldots,x_n,y_1,\ldots,y_m]$ is a finite extension, and so $\dim(A \otimes_k B) = n+m = \dim(A) + \dim(B)$, completing the proof.
\end{proof}
